\message{ !name(ms_vAA.tex)}% Use only LaTeX2e, calling the article.cls class and 12-point type.

\documentclass[12pt]{article}

% Users of the {thebibliography} environment or BibTeX should use the
% scicite.sty package, downloadable from *Science* at
% www.sciencemag.org/about/authors/prep/TeX_help/ .
% This package should properly format in-text
% reference calls and reference-list numbers.

\usepackage{scicite}

% Use times if you have the font installed; otherwise, comment out the
% following line.

\usepackage{times}

% The preamble here sets up a lot of new/revised commands and
% environments.  It's annoying, but please do *not* try to strip these
% out into a separate .sty file (which could lead to the loss of some
% information when we convert the file to other formats).  Instead, keep
% them in the preamble of your main LaTeX source file.


% The following parameters seem to provide a reasonable page setup.

\topmargin 0.0cm
\oddsidemargin 0.2cm
\textwidth 16cm 
\textheight 21cm
\footskip 1.0cm


%The next command sets up an environment for the abstract to your paper.

\newenvironment{sciabstract}{%
\begin{quote} \bf}
{\end{quote}}


% If your reference list includes text notes as well as references,
% include the following line; otherwise, comment it out.

\renewcommand\refname{References and Notes}

% The following lines set up an environment for the last note in the
% reference list, which commonly includes acknowledgments of funding,
% help, etc.  It's intended for users of BibTeX or the {thebibliography}
% environment.  Users who are hand-coding their references at the end
% using a list environment such as {enumerate} can simply add another
% item at the end, and it will be numbered automatically.

\newcounter{lastnote}
\newenvironment{scilastnote}{%
\setcounter{lastnote}{\value{enumiv}}%
\addtocounter{lastnote}{+1}%
\begin{list}%
{\arabic{lastnote}.}
{\setlength{\leftmargin}{.22in}}
{\setlength{\labelsep}{.5em}}}
{\end{list}}


% Include your paper's title here

\title{First discovery of variability of direct imaged exoplanet 2M1207b} 


% Place the author information here.  Please hand-code the contact
% information and notecalls; do *not* use \footnote commands.  Let the
% author contact information appear immediately below the author names
% as shown.  We would also prefer that you don't change the type-size
% settings shown here.

\author
{Yifan Zhou,$^{1\ast}$ Daniel Apai,$^{1}$ Glenn Schneider$^{1}$ Mark
  Marley$^{2}$ Adam Showman$^{3}$\\
\\
\normalsize{$^{1}$Department of Astronomy, the University of Arizona}\\
\normalsize{933 N. Cherry Ave., Tucson 85721, USA}\\
\normalsize{$^{2}$NASA Ames Research Center}\\
\normalsize{$^{3}$Department of Planetary Science, the University of Arizona}\\
\\
\normalsize{$^\ast$To whom correspondence should be addressed; E-mail:
  yifzhou@email.arizona.edu.}
}

% Include the date command, but leave its argument blank.

\date{}



%%%%%%%%%%%%%%%%% END OF PREAMBLE %%%%%%%%%%%%%%%%



\begin{document} 

\message{ !name(ms_vAA.tex) !offset(-3) }
 

% Double-space the manuscript.

\baselineskip24pt

% Make the title.

\maketitle 



% Place your abstract within the special {sciabstract} environment.

\begin{sciabstract}
Rotational modulations in disk-integrated light of
brown dwarfs have recently provided powerful constraints on the
properties of ultracool atmospheres, including longitudinal and
vertical cloud structures and cloud evolution. Furthermore, detection
of periodic light curve variations can directly probe the rotational
periods of ultracool objects. We present here, for the first time, time-resolved high-precision
photometric measurements of a planetary-mass companion, 2MASS1207b, to
a brown dwarf primary. Using HST/WFC3 and point spread function %in
combination with two spacecraft roll angles we detect photometric
modulations in the light curve. The amplitude is 0.9\% in the F160W
and 1.5\% in the F125W filters; we find a consistent period and
similar phase in both bands. Joint fit to the lightcurve in both bands
suggest a period of $10.2^{+0.9}_{-0.8}$ h. The relative amplitudes in the two
filters are very similar to that found in a recent study of a field
(high-gravity) L-dwarf, suggesting that the cloud structures that
introduce the photometric modulations are similar in high- and
low-gravity objects. Importantly, our study also measures, for the
first time, the rotational period for directly imaged planetary-mass
companion.
\end{sciabstract}

\textbf{Introduction}

\textbf{Observation}We obtained direct images of the 2M1207A+b
system on UT 2014 April 11from 08:07:47 to 16:53:18 using the Hubble
Space Telescope (HST) and its Wide Field Camera 3 \citep[WFC3,
][]{Kimble2008} in the frame of the HST Proposal GO-13418 (PI:
D. Apai). We acquired the observations in filters F125W
($\lambda_{\mbox{pivot}}$ = 1245.9 nm, full width at half maximum
(FWHM) = 301.5 nm) and F160W ($\lambda_{\mbox{pivot}}$ 1540.52, FWHM =
287.9 nm), roughly corresponding to the J and H bands. The WFC3 pixel
scale is $\approx$13mas. We used the $256\times256$ pixels sub-array
mode to avoid memory dumps during the observations.  In order to
provide a near-continuous coverage for detecting modulations we
observed the 2M1207 system in six consecutive HST orbits, obtaining
data with cadence of $\sim1.5$ minutes over a baseline of 8 hours and
40 minutes. The observations were interrupted by 58 minute-long Earth
occultations every 94 minutes.

\textbf{Data reduction}
\textbf{Hybrid PSF photometry}

One major challenge of high contrast imaging observation using WFC3/IR
is significant under-sampling of the detector.  2M1207 A and b are
only separated by $\sim6$ pixels or $\sim$5 FWHM of the PSF. When
applying roll subtraction, notable artifact structures are generated
by image interpolation and shifting. On the other hand, \tinytim{} PSF
simulator\citep{Krist1995} offers a solution by providing Nyquist or better
sampled PSF, but systematic errors of \tinytim{} PSF for WFC3 limits
its ability in high precision photometry\citep{Biretta2014}. However,
we are able to fully characterize the difference of model and observed
PSFs with 6 orbits time-resolved observation data. To obtain robust \tinytim{} PSF
photometry, we designed a 2-round PSF fitting strategy: 1. calculating
correction map for \tinytim{}; 2. hybrid PSF photometry.

For both of 2 rounds, we used {\em Tiny Tim} to calculate 10$\times$
over-sampled model PSFs based on the filters, the spectra 
\citep{Bonnefoy2014, Patience2010}, the telescope's actual focus, and
the telescope jitter.  We used the new set of Tiny Tim parameters
provided by \cite{Biretta2014} to improve model of the cold mask,
OTA spikes, and the coma. The focus parameters were calculated
using the model listed on the STScI
website\footnote{\url{http://www.stsci.edu/hst/observatory/focus/FocusModel}}. To
register \tinytim{} PSF to observed PSF of 2M1207A, we moved the
over-sampled PSF over a coordinate grid (gird size=0.001 pixel) using
cubic interpolation and minimize the rms difference of the
observed and re-binned \tinytim{} PSFs over a region centered on 2M1207A with a
5-pixel-radius aperture centered on 2M1207b excluded. Then we introduce
another \tinytim{} PSF for 2M1207b and  fit the
position of 2M1207 b and the photometries of 2M1207 A and b simultaneously
by least square optimization. From our data set, we discovered that
the difference of observed PSFs and model PSFs were very stable for
given PSF positions. Therefore at the end of the first round PSF
fitting, we derived 8 (2 roll angles $\times$ 4 dithering positions)
observationally derived correction maps for each filter:
\begin{equation}
  \mathrm{Corr = Median(PSF_{obs.} - PSF_{model} )}
\end{equation}
where $\mathrm{PSF_{model}}$ is a combination of two \tinytim{} PSFs
for 2M1207 A and b. In the second round, we combined the correction
term linearly with the two \tinytim{} PSFs to generate hybrid PSFs,
and fitted the three components together. We found that by including the correction term,
the reduced $\chi^{2}$ of PSF fitting is decreased from $\sim 10$ to
around unity. Relative photometry is acquired from the scaling
parameters of the model PSFs.

PSF profiles change with exposure positions due to
pixelation, especially for the case that WFC3 IR is significantly
under-sampled. Also, the flat fields may potentially have large scale
structures \citep{dressel2012wide}. We found a correlation of
photometry with PSF positions on detector frame for both 2M1207 A and
b. Correction were made by normalizing each group of
exposures that have the same dithering position and roll angle
individually -- we took the median of the fluxes that were measured
from these exposures as normalization factors and divided them from
every photometric measurement. Because the normalization factor for
each group of exposures is calculated across the whole observation,
this normalization step have negligible impacts on variability
analysis.


% In setting up this template for *Science* papers, we've used both
% the \section* command and the \paragraph* command for topical
% divisions.  Which you use will of course depend on the type of paper
% you're writing.  Review Articles tend to have displayed headings, for
% which \section* is more appropriate; Research Articles, when they have
% formal topical divisions at all, tend to signal them with bold text
% that runs into the paragraph, for which \paragraph* is the right
% choice.  Either way, use the asterisk (*) modifier, as shown, to
% suppress numbering.



\bibliography{ref.bib}

\bibliographystyle{Science}





\end{document}





















%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

\message{ !name(ms_vAA.tex) !offset(-264) }
